---
title: "groupwork"
author: "tamayo, loredo, parrenas"
date: "2024-04-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(ggplot2)
library(dplyr)
```
Read the Responses
```{r}
survey <- read_csv("Survey_ Understanding Student Engagement in Online Gaming.csv")
View(survey)
```
Mean of each columns
```{r}
numeric_cols <- sapply(survey, is.numeric) 

survey_numeric <- survey[, numeric_cols]

col_means <- colMeans(survey_numeric)
col_means
```

```{r}
age <- survey %>%
  mutate(Age = as.factor(Age)) %>%
  group_by(Age) %>%
  summarise(count = n())

# geting mean and standard deviation of counts
age_summary <- age %>%
  summarise(mean_count = mean(count),
            sd_count = sd(count))

ggplot(age, aes(x = Age, y = count)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Age", y = "Frequency", title = "Frequency of Age Groups")
```

Gender Responses
```{r}
gender <- table(survey$Gender)
 gender<- as.data.frame(gender)
 gender
 
 
 ggplot(gender, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "pink") +  
  labs(title = "Gender of Respondents", x = "Gender", y = "Frequency")
```

```{r}
address_data <- survey$Address 
addressdf <- data.frame(address = address_data)

addressdf$address <- toupper(trimws(addressdf$address))  

address_freq <- addressdf %>%
  group_by(address) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```
<<<<<<< HEAD

```{r}
#Plotting
ggplot(address_freq, aes(x = factor(address), y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "Address of Respondents", x = "Address", y = "Frequency") +
  theme(axis.text.x = element_text(angle =  , hjust =  ))
```
Gender Responses
```{r}
#geting the count of gender
(gender <- survey %>%
  mutate(Gender = as.character(Gender)) %>%  
  group_by(Gender) %>%
  summarise(count = n()))

# geting mean and standard deviation of counts
(gender_summary <- gender %>%
  summarise(mean_count = mean(count),
            sd_count = sd(count)))

ggplot(gender, aes(x = Gender, y = count)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.7) +
  labs(
    title = "Counts of Survey Respondents by Gender",
    x = "Gender",
    y = "Count"
  ) +
  theme_minimal()
```
Level of education
```{r}
year_level <- survey %>% 
  mutate(`Level of education you are currently in`) %>%
  group_by(`Level of education you are currently in`) %>%
  summarise(count = n())

# Mean and standard deviation
survey_year <- year_level %>%
  summarise(mean_count = mean(count),
            sd_count = sd(count))
#plotting
ggplot(year_level, aes(x = `Level of education you are currently in`, y = count)) +
  geom_bar(stat = "identity", fill = "pink", width = 0.1) +
  labs(x = "Level of Education", y = "Frequency", title = "Level of education you are currently in")
```
Name of Respondents
```{r}
name_data <- survey$`Name (optional)`
namedf <- data.frame(name = name_data) 

namedf$name <- toupper(trimws(namedf$name))  

```

```{r}
library(ggplot2)

question1 <- survey %>%
  mutate(`How confident are you that playing online games can help you develop valuable skills, such as problem-solving or teamwork?` = as.character(`How confident are you that playing online games can help you develop valuable skills, such as problem-solving or teamwork?`)) %>%  
  group_by(`How confident are you that playing online games can help you develop valuable skills, such as problem-solving or teamwork?`) %>%
  summarise(count = n())

# Mean and standard deviation
survey_summary <- question1 %>%
  summarise(mean_count = mean(count),
            sd_count = sd(count))

ggplot(question1, aes(x = `How confident are you that playing online games can help you develop valuable skills, such as problem-solving or teamwork?`, y = count)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Confidence Level", y = "Frequency", title = "How confident are you that playing online games can help you develop valuable skills, such as problem-solving or teamwork?")
```


```{r}
# Correct the column names in mutate and group_by functions
q2 <- survey %>%
  mutate(`Do you believe that playing online games can improve your cognitive abilities, like critical thinking or decision-making?`) %>%
  group_by(`Do you believe that playing online games can improve your cognitive abilities, like critical thinking or decision-making?`) %>%
    summarise(count = n())

# Calculate count, mean, and standard deviation
q2_summary <- q2 %>%
  summarise(mean_count = mean(count),
            sd_count = sd(count))
q2_summary

# Plotting
ggplot(q2, aes(x = `Do you believe that playing online games can improve your cognitive abilities, like critical thinking or decision-making?`, y = count)) +
  geom_bar(stat = "identity", width = 0.7, fill = "green") +
  geom_text(aes(label = count), vjust = -0.5) + 
  labs(title = "Do you believe that playing online games can improve your cognitive abilities, like critical thinking or decision-making?",
       x = "Cognitive Abilities",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")  # Remove legend


```

```{r}
q3 <- survey %>%
  mutate(`In your experience, have online games ever helped you achieve a specific goal or overcome a challenge (academic, social)?`) %>%
  group_by(`In your experience, have online games ever helped you achieve a specific goal or overcome a challenge (academic, social)?`) %>%
  summarise(count = n())

#get sd and mean
q3_summary <- q3 %>%
  summarise( mean_count = mean(count),
             sd_count = sd(count))

#plotting
ggplot(q3, aes(x = `In your experience, have online games ever helped you achieve a specific goal or overcome a challenge (academic, social)?`, y = count)) +
  geom_bar(stat = "identity", width = 0.7, fill = "blue") +
  geom_text(aes(label = count), vjust = -0.5) + 
  labs(title = "In your experience, have online games ever helped you achieve a specific goal or overcome a challenge (academic, social)? ",
       x = "Responses",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")  # Remove legend

```

```{r}
q4 <- survey %>%
  mutate(`How easy or difficult do you find it to learn the rules and mechanics of new online games?`) %>%
  group_by(`How easy or difficult do you find it to learn the rules and mechanics of new online games?`) %>%
  summarise(count = n())

#get mean and sd
q4_summary <- q4 %>%
  summarise(mean_count = mean(count),
            sd_count = sd(count))

#plotting
ggplot(q4, aes(x = `How easy or difficult do you find it to learn the rules and mechanics of new online games?`, y = count)) +
  geom_bar(stat = "identity", width = 0.7, fill = "skyblue") +
  geom_text(aes(label = count), vjust = -0.5) + 
  labs(title = "Effort Expectancy",
       x = "How easy or difficult do you find it to learn the rules and mechanics of new online games?",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")  # Remove legend
```

```{r}
q5 <- survey %>%
  mutate(`Do you feel that online games require a lot of time and effort to be successful or enjoyable?`) %>%
  group_by(`Do you feel that online games require a lot of time and effort to be successful or enjoyable?`) %>%
  summarise(count = n())


  geom_bar(stat = "identity", fill = "skyblue", width = 0.7) +
  labs(
    title = "Counts of Survey Respondents by Age",
    x = "Age",
    y = "Count"
  ) +
  theme_minimal()


#get mean and sd
q5_summary <- q5 %>%
  summarise(mean_count = mean(count),
            sd_count = sd(count))
q5_summary

#plotting
ggplot(q5, aes(x = `Do you feel that online games require a lot of time and effort to be successful or enjoyable?`, y = count)) +
  geom_bar(stat = "identity", width = 0.7, fill = "skyblue") +
  geom_text(aes(label = count), vjust = -0.5) + 
  labs(title = "Effort Expectancy",
       x = "Do you feel that online games require a lot of time and effort to be successful or enjoyable?",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")  # Remove legend
```
